R Notebook

### 2022-07-12 FEM_R/dfly_detailed_output.Rmd
Committing lots of changes over a long period of time. Lots of work towards the lockdown alcohol and minimum unit price interventions. Should have been better at committing this stuff but theres been a lot of switching between different ideas

```{r "setup", include=FALSE}
# Need to set up the environment
workingDir <- "/home/luke/Documents/E_FEM_clean/tmp_output/"
knitr::opts_knit$set(root.dir = workingDir)

require(tidyverse)
require(haven)
require(reshape2)
require(ggplot2)
require(ggpubr)
#require(plyr)
#require(data.table)

@@

```{r}
cohort <- read_dta('ELSA_core_cohort/ELSA_core_cohort_append.dta')
#heart <- read_dta('ELSA_core_remove_hearte_c/ELSA_core_remove_hearte_c_append.dta')
smok <- read_dta('ELSA_core_remove_smoken/ELSA_core_remove_smoken_append.dta')
```

@@

# generate flag for initial wave with disease and year died (if known)
new.c <- cohort %>%
          group_by(hhidpn, mcrep) %>%
          arrange(year, .by_group = TRUE) %>%
          mutate(hearte_init = min(year[hearte == 1]), hearte_died = max(year[hearte == 1])) %>%
          mutate(lunge_init = min(year[lunge == 1]), lunge_died = max(year[lunge == 1]))

# Replace all infinite values with 0 (infinites generated in mutate calls above)
new$hearte_init[is.infinite(new$hearte_init)] <- 0
new$hearte_died[is.infinite(new$hearte_died)] <- 0
new$lunge_init[is.infinite(new$lunge_init)] <- 0
new$lunge_died[is.infinite(new$lunge_died)] <- 0

>>>>

```{r "setup", include=FALSE}
# Need to set up the environment
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/"
knitr::opts_knit$set(root.dir = workingDir)

require(tidyverse)
require(haven)
#require(reshape2)
require(ggplot2)
#require(ggpubr)
#require(plyr)
#require(data.table)

@@

```{r}
#cohort <- read_dta('ELSA_core_cohort/ELSA_core_cohort_append.dta')
#heart <- read_dta('ELSA_core_remove_hearte_c/ELSA_core_remove_hearte_c_append.dta')
#smok <- read_dta('ELSA_core_remove_smoken/ELSA_core_remove_smoken_append.dta')

path <- 'input_data/detailed_output/'

cohort <- read_dta(paste0(path, 'ELSA_cohort_append.dta'))
mup <- read_dta(paste0(path, 'ELSA_alcInt_cohort_append.dta'))
```

@@

# generate flag for initial wave with disease and year died (if known)
new.c <- cohort %>%
          group_by(hhidpn, mcrep) %>%
          arrange(year, .by_group = TRUE) %>%
          mutate(hearte_init = min(year[hearte == 1]), hearte_died = max(year[hearte == 1])) %>%
          mutate(diabe_init = min(year[diabe == 1]), diabe_died = max(year[diabe == 1]))

# Replace all infinite values with 0 (infinites generated in mutate calls above)
new.c$hearte_init[is.infinite(new.c$hearte_init)] <- 0
new.c$hearte_died[is.infinite(new.c$hearte_died)] <- 0
new.c$diabe_init[is.infinite(new.c$diabe_init)] <- 0
new.c$diabe_died[is.infinite(new.c$diabe_died)] <- 0
